---
title: "lab 3 lk"
author: "Logan Kozal"
date: "1/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(jtools)
```

```{r}
penguins %>% 
  select(species, bill_length_mm:sex) %>% 
  ggpairs(aes(color=species))
```

Create a subset with only adelie and chinstrap penguins

```{r}
#species is a factor
adelie_chinstrap <- penguins %>% 
  filter(species %in% c("Adelie","Chinstrap")) %>% 
  mutate(species = fct_drop(species))

#Gentoo still shows up as a level  > fct_drop
```

Data vis of these two species

```{r}
ggplot(data = adelie_chinstrap, aes(x=body_mass_g, y=flipper_length_mm))+
  geom_point(aes(color = sex))+
  facet_wrap(~species)
```

Binary logistic regression 
- body mass
- flipper length
- penguin sex

```{r}
adelie_chinstrap_blr <- glm(species ~ body_mass_g + flipper_length_mm 
                            + sex,
                            data = adelie_chinstrap,
                            family="binomial")
```

Take a look at the outcomes

```{r}
adelie_chinstrap_blr

summary(adelie_chinstrap_blr)
#flipper length is significant
```

```{r}
ggplot(data = adelie_chinstrap, aes(x= species, y=flipper_length_mm))+
  geom_jitter(aes(color=sex))
```

What are the actual probablities of being chinstrap for each of the observations in our adelie_chinstrap dataframe? using broom

```{r}
blr_fitted <- adelie_chinstrap_blr %>% 
  broom::augment(type.predict = "response")
#fitted value is the probability based on our model that that penguin is a chinstrap
# We see that this is not perfect, can make a matrix of false positives, negatives, corrects
```

plotting fitted probailities:
```{r}
ggplot(data = blr_fitted, aes(x=flipper_length_mm, y=.fitted))+
  geom_point(aes(color=sex, pch = species))+
  geom_smooth(aes(color=sex), se=FALSE)+
  labs(x="Flipper Length(mm)", y="Probability of outcome Chinstrap")
#can see which ones would be likely to be miclassified
#geomsmooth is not showing out perfect model
```

#could add a layer where adelies are black dots at o and chinstraps are black dots at one, actual species


Plot model based on different variables:
effect_plot is from jtools

```{r}
effect_plot(adelie_chinstrap_blr,
            pred = flipper_length_mm,
            y.label = "Probability of Chinstrap",
            interval = TRUE)

effect_plot(adelie_chinstrap_blr,
            pred = body_mass_g,
            y.label = "Probability of Chinstrap",
            interval = TRUE)
```
What's the probability that a female penguin weighing 3410 g with a flipper length of 192mm is a chinstrap?

```{r}
#has to match model syntax and the factor levels of the model to work
ex_1 <- predict(adelie_chinstrap_blr,
                data.frame(sex = "female",
                           body_mass_g = 3410,
                           flipper_length_mm = 192),
                type = "response") # default is log odds so have to change to response to see probability

ex_1
```

